Scottish Child Payment Interventions

### 2024-01-16 minos/outcomes/CPR_vis.Rmd
Additions to the CPR and SCP vis scripts, and modified some of the datain functions to better handle batch files

# define subset of variables to reduce size of batch output
var.list <- c('pidp', 'hidp', 'time', 'weight', 
              'age', 'ethnicity', 'education_state', 'region', 
              'hh_income',
              'housing_quality', 'neighbourhood_safety', 'loneliness', 'ncigs', 'nutrition_quality', 'financial_situation', 'urban', 'housing_tenure',
              'SF_12', 'matdep_child')

base <- read_output(out.path, 
                        scenario = 'baseline', 
                        var.list = var.list,
                        verbose = TRUE)
int <- read_output(out.path, 
                            scenario = 'ChildPovertyReductionSUSTAIN', 
                            var.list = var.list,
                            verbose = TRUE)
```

@@

print(paste0("Relative poverty threshold in 2020: ", rel.pov.threshold))
rm(base.2020, mean.hh_income, rel.pov.threshold)
```

@@

ggplot(data = threshold, aes(x = time, y = poverty_threshold)) +
  geom_col() +
  geom_hline(yintercept = threshold$poverty_threshold[threshold$time == 2020], linetype='dashed') +
  labs(title = 'Relative poverty threshold over time') +
  xlab('Year') +
  ylab('Threshold')
```

@@

```{r}
full.sample.change.SF12 <- function(base.dat, int.dat) {
  base.all.SF12 <- base.dat %>%
    select(time, weight, SF_12) %>%
    group_by(time) %>%
    summarise(base.SF12 = weighted.mean(SF_12, w = weight))

  ggplot(combined, aes(x = time, y = diff)) +
    geom_line() +
    geom_hline(yintercept = 0, linetype='dashed') +
    labs(title = 'Relative change in SF12') +
    xlab('Year') +
    ylab('Difference')
}

full.sample.change.SF12(base, int)
```

>>>>

# define subset of variables to reduce size of batch output
var.list <- c('pidp', 'hidp', 'time', 'weight', 
              'age', 'ethnicity', 'education_state', 'region', 'nkids',
              'hh_income',
              'housing_quality', 'neighbourhood_safety', 'loneliness', 'ncigs', 'nutrition_quality', 'financial_situation', 'urban', 'housing_tenure',
              'SF_12', 'matdep_child')

base <- read_output(out.path, 
                        scenario = 'baseline', 
                        var.list = var.list,
                        verbose = TRUE)
int <- read_output(out.path, 
                            scenario = 'ChildPovertyReductionSUSTAIN', 
                            var.list = var.list,
                            verbose = TRUE)

# base$income_boosted <- FALSE
# base$boost_amount <- 0

# set up a boolean tag for batch or not
# this is necessary because batch runs need slightly different processing before visualisation
if ('run_id' %in% names(base)) {
  batch <- TRUE
} else {
  batch <- FALSE
}

# Save path and save flag
save.path <- here::here('plots', 'SCOTGOV', 'CPR')
shall.we.save <- FALSE
plot.width <- 10
plot.height <- 5
```

# FUNCTIONS

```{r SF12_full_sample, echo=FALSE}
SF12.change.full.sample.single <- function(base.dat, int.dat) {
  base.all.SF12 <- base.dat %>%
    select(time, weight, SF_12) %>%
    group_by(time) %>%
    summarise(base.SF12 = weighted.mean(SF_12, w = weight))

  p1 <- ggplot(combined, aes(x = time, y = diff)) +
    geom_line() +
    geom_hline(yintercept = 0, linetype='dashed') +
    labs(title = 'Relative change in SF12', subtitle = 'Whole population') +
    xlab('Year') +
    ylab('Difference')

  print(p1)

  if (shall.we.save) {
    filename <- paste0(save.path, 'SF12_whole_pop_single.png')

    ggsave(filename = filename,
           plot = p1,
           width = plot.width,
           height = plot.height)
  }
}

SF12.change.full.sample.batch <- function(base.dat, int.dat, batch) {
  base.all.SF12 <- base.dat %>%
    select(time, weight, run_id, SF_12) %>%
    group_by(time, run_id) %>%
    summarise(base.SF12 = weighted.mean(SF_12, w = weight))

  int.all.SF12 <- int.dat %>%
    select(time, weight, run_id, SF_12) %>%
    group_by(time, run_id) %>%
    summarise(int.SF12 = weighted.mean(SF_12, w = weight))

  combined <- merge(x = base.all.SF12, y = int.all.SF12, by = c('time', 'run_id'))
  combined$diff <- combined$int.SF12 - combined$base.SF12

  p1 <- ggplot(combined, aes(x = time, y = diff)) +
    geom_smooth() +
    geom_hline(yintercept = 0, linetype='dashed') +
    labs(title = 'Relative change in SF12', subtitle = 'Whole population') +
    xlab('Year') +
    ylab('Difference')

  print(p1)

  if (shall.we.save) {
    filename <- paste0(save.path, 'SF12_whole_pop_batch.png')
    ggsave(filename = filename,
           plot = p1,
           width = plot.width,
           height = plot.height)
  }
}
```

```{r SF12_subpop, echo=FALSE}
SF12.change.families.single <- function(base.dat, int.dat) {
  base.all.SF12 <- base.dat %>%
    select(time, weight, SF_12, nkids) %>%
    filter(nkids > 0) %>%
    group_by(time) %>%
    summarise(base.SF12 = weighted.mean(SF_12, w = weight))

  int.all.SF12 <- int.dat %>%
    select(time, weight, SF_12, nkids) %>%
    filter(nkids > 0) %>%
    group_by(time) %>%
    summarise(int.SF12 = weighted.mean(SF_12, w = weight))

  p1 <- ggplot(combined, aes(x = time, y = diff)) +
    geom_line() +
    geom_hline(yintercept = 0, linetype='dashed') +
    labs(title = 'Relative change in SF12', subtitle = 'Families with children') +
    xlab('Year') +
    ylab('Difference')

  print(p1)

  if (shall.we.save) {
    filename <- paste0(save.path, 'SF12_families_single.png')

    ggsave(filename = filename,
           plot = p1,
           width = plot.width,
           height = plot.height)
  }
}

SF12.change.families.batch <- function(base.dat, int.dat) {
  base.all.SF12 <- base.dat %>%
    select(time, weight, run_id, SF_12, nkids) %>%
    filter(nkids > 0) %>%
    group_by(time, run_id) %>%
    summarise(base.SF12 = weighted.mean(SF_12, w = weight))

  int.all.SF12 <- int.dat %>%
    select(time, weight, run_id, SF_12, nkids) %>%
    filter(nkids > 0) %>%
    group_by(time, run_id) %>%
    summarise(int.SF12 = weighted.mean(SF_12, w = weight))

  p1 <- ggplot(combined, aes(x = time, y = diff)) +
    geom_smooth() +
    geom_hline(yintercept = 0, linetype='dashed') +
    labs(title = 'Relative change in SF12', subtitle = 'Families with children') +
    xlab('Year') +
    ylab('Difference')

  print(p1)

  if (shall.we.save) {
    filename <- paste0(save.path, 'SF12_families_batch.png')
    ggsave(filename = filename,
           plot = p1,
           width = plot.width,
           height = plot.height)
  }
}
```

```{r SF12_treated, echo=FALSE}
SF12.change.treated.single <- function(base.dat, int.dat) {
  boosted.byyear <- int.dat %>%
    filter(income_boosted == 'True')

  base.all.SF12 <- base.dat %>%
    select(time, weight, SF_12, nkids, pidp) %>%
    filter(pidp %in% boosted.byyear$pidp) %>%
    group_by(time) %>%
    summarise(base.SF12 = weighted.mean(SF_12, w = weight))

  int.all.SF12 <- int.dat %>%
    select(time, weight, SF_12, nkids, pidp) %>%
    filter(pidp %in% boosted.byyear$pidp) %>%
    group_by(time) %>%
    summarise(int.SF12 = weighted.mean(SF_12, w = weight))

  p1 <- ggplot(combined, aes(x = time, y = diff)) +
    geom_line() +
    geom_hline(yintercept = 0, linetype='dashed') +
    labs(title = 'Relative change in SF12', subtitle = 'Treatment on the treated') +
    xlab('Year') +
    ylab('Difference')

  print(p1)

  if (shall.we.save) {
    filename <- paste0(save.path, 'SF12_treated_single.png')
    ggsave(filename = filename,
           plot = p1,
           width = plot.width,
           height = plot.height)
  }
}

SF12.change.treated.batch <- function(base.dat, int.dat) {

  #TODO: Filter pidps by run_id by year instead of taking all pidps across runs
  boosted.byyear <- int.dat %>%
    filter(income_boosted == 'True')

  base.all.SF12 <- base.dat %>%
    select(time, weight, run_id, SF_12, nkids, pidp) %>%
    filter(pidp %in% boosted.byyear$pidp) %>%
    group_by(time, run_id) %>%
    summarise(base.SF12 = weighted.mean(SF_12, w = weight))

  int.all.SF12 <- int.dat %>%
    select(time, weight, run_id, SF_12, nkids, pidp) %>%
    filter(pidp %in% boosted.byyear$pidp) %>%
    group_by(time, run_id) %>%
    summarise(int.SF12 = weighted.mean(SF_12, w = weight))

  combined <- merge(x = base.all.SF12, y = int.all.SF12, by = c('time', 'run_id'))
  combined$diff <- combined$int.SF12 - combined$base.SF12

  p1 <- ggplot(combined, aes(x = time, y = diff)) +
    geom_smooth() +
    geom_hline(yintercept = 0, linetype='dashed') +
    labs(title = 'Relative change in SF12', subtitle = 'Treatment on the treated') +
    xlab('Year') +
    ylab('Difference')

  print(p1)

  if (shall.we.save) {
    filename <- paste0(save.path, 'SF12_treated_single.png')
    ggsave(filename = filename,
           plot = p1,
           width = plot.width,
           height = plot.height)
  }
}
```

@@

print(paste0("Relative poverty threshold in 2020: ", rel.pov.threshold))
rm(base.2020, mean.hh_income)
```

@@

ggplot(data = threshold, aes(x = time, y = poverty_threshold)) +
  geom_col() +
  geom_hline(yintercept = rel.pov.threshold, linetype='dashed') +
  labs(title = 'Relative poverty threshold over time') +
  xlab('Year') +
  ylab('Threshold')

threshold <- base %>%
  select(time, weight, run_id, hh_income) %>%
  group_by(time, run_id) %>%
  summarise(poverty_threshold = (weighted.mean(hh_income, w = weight) * 0.6)) %>%
  group_by(time) %>%
  summarise(poverty_threshold_mean = mean(poverty_threshold),
            lower = min(poverty_threshold),
            upper = max(poverty_threshold))

ggplot(data = threshold, aes(x = time, y = poverty_threshold_mean)) +
  geom_col() +
  geom_errorbar(aes(ymin = lower, ymax = upper), position = 'dodge') +
  geom_hline(yintercept = rel.pov.threshold, linetype='dashed') +
  labs(title = 'Relative poverty threshold over time') +
  xlab('Year') +
  ylab('Threshold')
```

@@

```{r}
if (batch) {
  SF12.change.full.sample.batch(base, int)
} else {
  SF12.change.full.sample.single(base, int)
}
```

### MCS - Families with children

Now focused only on families with children.

```{r}
if (batch) {
  SF12.change.families.batch(base, int)
} else {
  SF12.change.families.single(base, int)
}
```

### MCS - Treatment on the Treated

```{r}
if (batch) {
  SF12.change.treated.batch(base, int)
} else {
  SF12.change.treated.single(base, int)
}
```

### 2024-01-16 minos/outcomes/SCP_vis.Rmd
Additions to the CPR and SCP vis scripts, and modified some of the datain functions to better handle batch files

```{r}
out.path <- here::here('output', 'default_config')

# define subset of variables to reduce size of batch output
var.list <- c('pidp', 'hidp', 'time', 'weight', 
              'age', 'ethnicity', 'education_state', 'region', 
              'hh_income',
              'housing_quality', 'neighbourhood_safety', 'loneliness', 'ncigs', 'nutrition_quality', 'financial_situation', 'urban', 'housing_tenure',
              'SF_12', 'matdep_child')

@@

int.list <- c(int25All, int50All, int75All, int100All)
```

@@

```{r}
full.sample.change.SF12 <- function(base.dat, int.dat) {
  base.all.SF12 <- base.dat %>%
    select(time, weight, SF_12) %>%
    group_by(time) %>%
    summarise(base.SF12 = weighted.mean(SF_12, w = weight))

@@

>>>>

```{r}
out.path <- here::here('output', 'default_config_batch')

# define subset of variables to reduce size of batch output
var.list <- c('pidp', 'hidp', 'time', 'weight', 
              'age', 'ethnicity', 'education_state', 'region', 'nkids',
              'hh_income',
              'housing_quality', 'neighbourhood_safety', 'loneliness', 'ncigs', 'nutrition_quality', 'financial_situation', 'urban', 'housing_tenure',
              'SF_12', 'matdep_child')

@@

int.list <- c(int25All, int50All, int75All, int100All)

# set up a boolean tag for batch or not
# this is necessary because batch runs need slightly different processing before visualisation
if ('run_id' %in% names(base)) {
  batch <- TRUE
} else {
  batch <- FALSE
}

# Save path and save flag
save.path <- here::here('plots', 'SCOTGOV', 'CPR')
shall.we.save <- FALSE
plot.width <- 10
plot.height <- 5
```

@@

```{r}
SF12.change.full.sample.single <- function(base.dat, int.dat1, int.dat2, int.dat3, int.dat4) {
  base <- base.dat %>%
    select(time, weight, SF_12) %>%
    group_by(time) %>%
    summarise(base.SF12 = weighted.mean(SF_12, w = weight))

  int1 <- int.dat1 %>%
    select(time, weight, SF_12) %>%
    group_by(time) %>%
    summarise(int1.SF12 = weighted.mean(SF_12, w = weight))
  int2 <- int.dat2 %>%
    select(time, weight, SF_12) %>%
    group_by(time) %>%
    summarise(int2.SF12 = weighted.mean(SF_12, w = weight))
  int3 <- int.dat3 %>%
    select(time, weight, SF_12) %>%
    group_by(time) %>%
    summarise(int3.SF12 = weighted.mean(SF_12, w = weight))
  int4 <- int.dat4 %>%
    select(time, weight, SF_12) %>%
    group_by(time) %>%
    summarise(int4.SF12 = weighted.mean(SF_12, w = weight))

  # now combine all data together and calculate differences
  combined <- merge(x = base, y = int1, by = 'time')
  combined <- merge(x = merged, y = int2, by = 'time')
  combined <- merge(x = merged, y = int3, by = 'time')
  combined <- merge(x = merged, y = int4, by = 'time')

  combined$diff <- combined$int.SF12 - combined$base.SF12

```{r}
SF12.change.full.sample.single <- function(base.dat, int.dat) {
  base.all.SF12 <- base.dat %>%
    select(time, weight, SF_12) %>%
    group_by(time) %>%
    summarise(base.SF12 = weighted.mean(SF_12, w = weight))

@@

  p1 <- ggplot(combined, aes(x = time, y = diff)) +
    geom_line() +
    geom_hline(yintercept = 0, linetype='dashed') +
    labs(title = 'Relative change in SF12', subtitle = 'Whole population') +
    xlab('Year') +
    ylab('Difference')

  print(p1)

  if (shall.we.save) {
    filename <- paste0(save.path, 'SF12_whole_pop_single.png')

    ggsave(filename = filename,
           plot = p1,
           width = plot.width,
           height = plot.height)
  }
}

SF12.change.full.sample.batch <- function(base.dat, int.dat, batch) {
  base.all.SF12 <- base.dat %>%
    select(time, weight, run_id, SF_12) %>%
    group_by(time, run_id) %>%
    summarise(base.SF12 = weighted.mean(SF_12, w = weight))

  int.all.SF12 <- int.dat %>%
    select(time, weight, run_id, SF_12) %>%
    group_by(time, run_id) %>%
    summarise(int.SF12 = weighted.mean(SF_12, w = weight))

  combined <- merge(x = base.all.SF12, y = int.all.SF12, by = c('time', 'run_id'))
  combined$diff <- combined$int.SF12 - combined$base.SF12

  p1 <- ggplot(combined, aes(x = time, y = diff)) +
    geom_smooth() +
    geom_hline(yintercept = 0, linetype='dashed') +
    labs(title = 'Relative change in SF12', subtitle = 'Whole population') +
    xlab('Year') +
    ylab('Difference')

  print(p1)

  if (shall.we.save) {
    filename <- paste0(save.path, 'SF12_whole_pop_batch.png')
    ggsave(filename = filename,
           plot = p1,
           width = plot.width,
           height = plot.height)
  }
}
```
